\section{Introduction}
\label{sec:intro}

LLMs are increasingly applied to financial tasks, but the dominant evaluation paradigm targets \emph{comprehension} of already-prepared artifacts. FinQA \citep{chen-etal-2021-finqa}, ConvFinQA \citep{chen-etal-2022-convfinqa}, TAT-QA \citep{zhu-etal-2021-tatqa}, and DocFinQA \citep{reddy-etal-2024-docfinqa} pose numerical questions over excerpted tables and text. FinanceBench \citep{islam2023financebench}, FinanceMATH \citep{zhao-etal-2024-financemath}, FinBen \citep{xie2024finben}, and FinAuditing \citep{wang2026finauditing} test analysis or auditing over prepared statements. In each case the financial statement already exists; the model reasons \emph{over} it.

\input{tables/prior_work_comparison}

Real accounting workflows begin one step earlier. A bundle of source documents---invoices, bank statements, payment notices, contracts, schedules, exemption certificates---must be reconciled: each transaction extracted as a balanced journal entry citing its supporting documents, the entries aggregated into a balance sheet that respects the accounting equation, and contradictions among documents detected and classified rather than silently resolved. We introduce \benchmark{}, a multi-document accounting reconciliation benchmark built from source-document bundles with OCR text across eight industries, three period types, and five difficulty levels, with concept-coverage flags for revenue recognition under ASC~606, leases, deferred tax, asset disposals, multi-jurisdictional sales tax, foreign-currency remeasurement, and tax exemptions.

\benchmark{} is both a benchmark resource and a diagnostic testbed. The resource itself is nontrivial: it requires explicit modeling of business processes, evidence documents, accounting policy, document dependencies, distractors, and contradiction types before any data can be generated. This makes the benchmark a useful controlled prerequisite for real deployment: if a model cannot reconcile clean, fully specified document bundles with exact ground truth, it is unlikely to be reliable on real accounting work, where layouts, OCR, missing evidence, policy choices, and institutional conventions are messier. We therefore pair the release with our own evaluation suite---six contemporary-model baselines, citation ablations, context-vs.-logic stress tests, passive-tool tests, best-of-3 selection, and a forced ledger-feedback diagnostic---to show what current models can and cannot do on this document-grounded accounting task. In this evaluated panel, the benchmark is already challenging: the highest exact final-balance-sheet score is 51\%, and strict document-grounded end-to-end accuracy remains low.

\benchmark{} is synthetic by construction, but its accounting knowledge is human-authored rather than model-invented. We first spend the design effort where accountants would: defining business scenarios across industries, document schemas, a chart of accounts, accounting policies, tax and FX treatments, support-document dependencies, distractor templates, and contradiction templates. These specifications define the space of valid records and the boundaries of amounts, dates, counterparties, document roles, and scenario combinations. The generator then performs the repetitive composition step: it samples from this human-written accounting specification, fills document fields, selects compatible evidence and distractors, renders source documents with OCR text, and uses the fixed double-entry ledger to compute the expected journal entries and balance sheet. This makes it possible to create many controlled combinations that would be expensive to hand-author one by one, while retaining exact labels: every expected entry, balance sheet, opening trial balance, and inconsistency code is computable, auditable, and reproducible from the specification.

We report two complementary balance-sheet metrics. \bsexact{} measures whether the model's own self-reported balance sheet matches ground truth exactly. \bsrecon{} instead parses the journal entries produced by the model, applies those entries to the opening balance using our deterministic ledger, and checks whether the resulting balance sheet matches ground truth. The two diverge when the model writes entries with the right accounts and amounts, but its self-aggregated balance sheet is wrong. Evaluating six contemporary LLMs (Gemini~3 Flash, GPT-5, Claude Haiku~4.5, Grok-4.3, DeepSeek V3.2, Qwen~3 235B) yields three findings. \textbf{(i)}~An \aggGap{}: four of six show $25$--$38$\,pp between \bsrecon{} and \bsexact{}. The remaining two lack the gap for qualitatively different reasons---the highest-\bsexact{} run is genuinely self-consistent, while Grok-4.3 reports too few entries (only 40\% of the expected count), making its balance sheet more internally aligned but incomplete (\S\ref{sec:analysis}). \textbf{(ii)}~Document-linking is the dominant entry-level failure: 52\% of journal entries with correct account and amount cite the wrong documents, a rate that barely moves under explicit citation-pressure prompting ($-1.4$\,pp), implicating retrieval-disambiguation rather than prompt compliance. \textbf{(iii)}~When we use the deterministic ledger as a diagnostic tool and return its balance-sheet deltas to the model, \bsexact{} rises by $+25$ to $+37$\,pp across four model families; the same tool feedback also reveals a trade-off, degrading inconsistency-code detection by $-13$ to $-61$\,pp on smaller models.

\textbf{Contributions.}
\textbf{(1)}~A multi-document accounting reconciliation benchmark with deterministic ground truth, 23 inconsistency codes, and a released generator for fresh stratified samples. \textbf{(2)}~A six-model evaluation revealing a self-consistency \aggGap{}, with the highest evaluated model reaching 51\% \bsexact{}. \textbf{(3)}~A diagnostic ablation suite covering citation pressure, context stress, passive tools, best-of-3 selection, and forced ledger feedback. \textbf{(4)}~Expert validation by practising finance professionals, including an independently double-reviewed subset.
