\section{Related Work}

A growing body of financial natural language processing benchmarks has
emerged, but nearly all of them evaluate \emph{comprehension} over
existing reports rather than \emph{construction} of new accounting
artifacts.
FinQA~\citep{chen2021finqa} and
ConvFinQA~\citep{chen2022convfinqa} study numerical reasoning over
earnings reports;
TAT-QA~\citep{zhu2021tatqa} extends the setting to joint table--text
reasoning; and
DocFinQA~\citep{reddy2024docfinqa} situates similar questions within
long-form SEC filings.
These benchmarks require models to read a financial document and answer
questions about it, but not to construct a balance sheet from raw
transactions.

Broader financial evaluation suites such as
FLUE~\citep{shah2022flueflang},
PIXIU~\citep{xie2023pixiu},
FinBen~\citep{xie2024finben}, and
FinanceBench~\citep{islam2023financebench} span tasks including
sentiment analysis, named-entity recognition, market prediction, and
open-book question answering.
Reasoning-centric datasets such as
BizBench~\citep{krumdick2024bizbench},
FinanceMATH~\citep{zhao2024financemath}, and
XFinBench~\citep{zhang2025xfinbench} emphasize quantitative or
knowledge-intensive finance problems, often with exact answer checking,
but they still evaluate question answering or program synthesis rather
than artifact construction from raw accounting events.
More recent benchmark suites continue the broad-coverage trend:
BizFinBench~\citep{lu2025bizfinbench} expands to business-driven
financial tasks, FinDABench~\citep{liu2025findabench} studies financial
data-analysis ability, INVESTORBENCH~\citep{li2025investorbench}
targets agentic financial decision-making, FinTrust~\citep{hu2025fintrust}
evaluates trustworthiness in finance settings, Golden
Touchstone~\citep{wu2025goldentouchstone} emphasizes bilingual financial
NLP evaluation, and FinMaster~\citep{jiang2025finmaster} broadens the
scope to full-pipeline financial workflows.
These benchmarks cover important parts of financial language
understanding and decision support, yet they do not isolate end-to-end
accounting statement preparation under hard bookkeeping invariants.
Even MMLU~\citep{hendrycks2021mmlu}, which includes
professional-accounting questions, measures declarative knowledge in a
multiple-choice format rather than procedural bookkeeping.

The closest adjacent line of work studies richer financial analysis
over existing statements or filings rather than bookkeeping from raw
events.
SECQUE~\citep{benyoash2025secque} evaluates real-world financial
analysis over SEC documents; FinAR-Bench~\citep{wu2025finarbench}
focuses on fundamental-analysis competence; FinAuditing
~\citep{wang2025finauditing} studies taxonomy-structured auditing over
multi-document financial disclosures; and FinRule-Bench
~\citep{malarkkan2026finrulebench} evaluates joint reasoning over
financial tables and accounting principles.
Wang et al.~\citep{wang2025automating} also study automated financial
statement auditing with a benchmark that combines financial tables and
synthesized transaction data.
These tasks are closer to professional finance workflows than QA alone,
but they primarily begin from prepared financial artifacts and evaluate
analysis, diagnosis, or revision rather than direct construction of the
final statement from journal entries and adjustments.
More general multi-step arithmetic benchmarks such as
GSM8K~\citep{cobbe2021gsm8k} test quantitative reasoning, but they do
not impose the domain-specific conservation constraints, section
structure, and closing-entry behavior required in accounting.

\input{tables/prior_work_comparison}

Our benchmark therefore occupies a distinct point in the literature.
It evaluates whether a model can transform raw accounting events into a
complete, internally consistent balance sheet with exact ground truth.
That setting matters because exact invariants reveal failures that are
easy to hide in answer-only evaluation: a model may recover the right
accounts, sections, and financial vocabulary while still breaking the
accounting equation or mishandling equity closure.
