\section{Related Work}
\label{sec:related}

\paragraph{Financial-NLP question answering.}
FinQA \citep{chen-etal-2021-finqa} and ConvFinQA \citep{chen-etal-2022-convfinqa} pose numerical questions over single financial reports and their tabular content, with the latter requiring conversational multi-turn reasoning. TAT-QA \citep{zhu-etal-2021-tatqa} similarly evaluates models on hybrid tabular-and-text questions over filings. DocFinQA \citep{reddy-etal-2024-docfinqa} extends this paradigm to longer financial documents, and MultiHiertt \citep{zhao-etal-2022-multihiertt} targets reasoning over multiple hierarchical tables and accompanying text. These benchmarks share the assumption that a structured artifact---a table extracted from a filing, a single report---already exists, and the model's task is to answer questions \emph{over} it. \benchmark{} differs structurally: there is no prepared statement, only a packet of raw OCR-style documents from which the statement must be constructed.

\paragraph{Broader financial benchmarks and reconciliation-adjacent tasks.}
FinanceBench \citep{islam2023financebench} evaluates models on open-ended questions answerable from prepared SEC filings, testing analysis and judgment rather than construction. FinanceMATH \citep{zhao-etal-2024-financemath} targets knowledge-intensive math reasoning grounded in finance. FinBen \citep{xie2024finben} aggregates 42 datasets spanning information extraction, textual analysis, QA, generation, risk management, and forecasting, but excludes statement construction. Most closely related, FinAuditing \citep{wang2026finauditing} introduces a financial-taxonomy-structured multi-document benchmark for auditing-style tasks; like prior work, however, it evaluates models against prepared, taxonomy-tagged statements rather than asking them to reconcile raw documents into entries. BloombergGPT \citep{wu2023bloomberggpt} demonstrates that domain-tuned LLMs outperform general models on standard financial tasks but does not address reconciliation. \benchmark{} fills a gap in this landscape: a benchmark whose ground truth is a deterministically computed double-entry ledger and which exposes the consistency between journal entries and their aggregated balance sheet as a measurable quantity.

\paragraph{Self-consistency, refinement, and verifier-style interventions.}
Self-consistency \citep{wang2023selfconsistency} improves reasoning by sampling multiple chains and aggregating via majority vote. Self-Refine \citep{madaan2023selfrefine} and Reflexion \citep{shinn2023reflexion} use the language model itself as a feedback source, iterating on its own outputs. A parallel line trains explicit verifiers: outcome-supervised verifiers for math word problems \citep{cobbe2021gsm8k} and step-wise process reward models \citep{lightman2024verify} require labeled supervision and a separate verifier model. Our \verifier{} differs in two ways. First, it is \emph{rule-based and training-free}: the deterministic double-entry ledger that produces our ground truth is also the verifier, so feedback is closed-form rather than learned. Second, it operates one-shot at inference time without sampling overhead. The intervention's success across four model families with no fine-tuning suggests that the \aggGap{} is a process failure addressable by light deterministic scaffolding, complementing the parametric-improvement perspective of learned verifiers.

\paragraph{Long-context, document evidence, and tool use.}
\citet{liu2024lostmiddle} document a U-shaped accuracy curve as the position of relevant evidence varies within long contexts---directly relevant to our context-stress findings (\S\ref{sec:results}), where placing supporting documents at the end of the packet differentially affects inconsistency detection. Retrieval-augmented approaches \citep{lewis2020rag} address related document-grounding challenges; our \emph{evidence-only} ablation reports an oracle-retrieval upper bound. Finally, ReAct \citep{yao2023react} demonstrated the value of interleaving reasoning with tool calls; we observe in our setting that models bypass offered tools and emit final answers directly, motivating the forced-feedback design of our verifier intervention.

\input{tables/prior_work_comparison}
