\section{Experimental Setup}

\subsection{Evaluation Tiers}

The benchmark release contains 2{,}500 problems, but not every model
should be evaluated on the same subset size.
We therefore distinguish two reporting tiers.

\paragraph{Controlled-100.}
The main cross-model comparison in this draft uses a stratified
100-problem subset with 20 problems from each of the five difficulty
levels.
This tier is appropriate for expensive closed-source systems and large
open-weight systems because it keeps the comparison paired and
affordable while preserving coverage across the full difficulty range.
All main-paper model comparisons are reported on this identical split.

\paragraph{Large-500.}
For smaller open-weight models, the target evaluation protocol is a
500-problem subset with 100 problems from each difficulty level.
This larger tier is important for statistical credibility: claims about
model ranking, robustness, and prompt sensitivity are considerably more
defensible once they are supported by 500 or more benchmark instances.
The present manuscript defines this tier explicitly because a final
submission should not rely on 100-problem evidence alone when cheaper
models can be evaluated at larger scale.

\subsection{Controlled Models}

On the Controlled-100 split, we evaluate paired
\zs{}/\CoT{}~\citep{wei2022chainofthought} runs for six model
families: GPT-5.2, Gemini~3 Flash, Qwen~3.5 Flash, gpt-oss-120b,
DeepSeek-v3.2, and Llama~3.3~70B.
This is the only setting in the paper where all of these systems are
directly comparable on exactly the same 100 problems.

\subsection{Evaluation Harness}

The evaluation harness is automated and flexible: it instantiates a
model backend, applies a selected prompting strategy, parses the raw
response with multiple JSON-recovery rules, computes the full metric
suite, attaches an error report, and stores per-problem outputs for
later analysis.
Because prompting strategies, retry behavior, and model backends are
decoupled, the same harness supports controlled comparisons without
changing the benchmark instances or scoring logic.
For non-\zs{} conditions, the harness retries once with a \zs{}
prompt if the initial parse fails.
This distinction matters for interpretation: for some models,
especially gpt-oss-120b and Llama~3.3~70B, part of the measured
\CoT{} gain arises because the prompt is more likely to elicit a
parseable final JSON object after an otherwise malformed response,
rather than because it improves transaction posting or closing logic.
Prompt-level improvements should therefore not be interpreted
uniformly as evidence of stronger accounting reasoning.

All runs use deterministic decoding settings with temperature fixed at
\(0\).
A rule-based baseline provides an oracle-style upper bound and reaches a
FinBalance Score of \(99.97\) on the held-out Controlled-100 split.

\subsection{Statistical Reporting}

Three result summaries are especially important for the paper:
leaderboard metrics, analysis outputs covering factor sensitivity and
difficulty curves, and a significance summary with bootstrap confidence
intervals and paired permutation tests.
The current significance file covers only a subset of model pairs, so
the paper treats some comparisons as descriptive rather than
inferential.
Where exact \(p\)-values are cited below, they come directly from the
paired permutation tests on the Controlled-100 split (\(n=100\)).

More broadly, the statistical interpretation of the benchmark should
follow the evaluation tier.
The Controlled-100 split supports careful paired comparisons on a common
set of expensive runs, but it is not the final word on model ranking.
Whenever a smaller open-weight model can be run at acceptable cost, the
benchmark should instead report Large-500 results so that conclusions
rest on at least 500 problems.
