\section{Experimental Setup}
\label{sec:setup}

\paragraph{Models and decoding.}
We evaluate six contemporary LLMs: Gemini~3 Flash (anchor; full ablation matrix), GPT-5 (low reasoning effort for cost-controlled coverage), Claude Haiku~4.5, Grok-4.3, Qwen~3 235B, and DeepSeek Chat. This panel is intended to cover a range of closed, open, general-purpose, and cost profiles. All six receive the full main evaluation split ($n{=}710$) at baseline. To control API cost while preserving coverage, the ledger-feedback diagnostic and other targeted ablations are run on the compact $143$-record ablation split, where every industry-period-difficulty cell and every inconsistency code is represented at least once. Decoding uses temperature $0.0$, except best-of-3 selection (temperature $0.7$, three samples).

\paragraph{Ablations and bootstrap.}
We run four ablation families and report all effects against the same-model baseline: \textbf{(1) Prompt} tests guided solving, self-checking, and stronger citation instructions; model behavior is comparatively less sensitive to these prompt changes. \textbf{(2) Visibility} removes the account list, support documents, metadata, or non-evidence documents; these runs show that accounts and support evidence are necessary, and that oracle evidence helps document grounding. \textbf{(3) Context stress} tests whether errors come from longer context or from the harder accounting logic itself by adding distractors or moving relevant evidence later; the results indicate that context hurts, but that the task remains hard even when context is controlled. \textbf{(4) Tool/repair} tests calculators, search, the ledger-feedback tool, and best-of-3 sampling; passive tools are rarely used, while ledger feedback repairs many reported balance sheets but weakens inconsistency detection. Appendix~\ref{appx:ablation-grid} gives the full grid. For uncertainty, we resample record IDs $5000$ times and recompute each baseline--ablation difference on the same resampled records, yielding intervals for \bsexact{}, \bsrecon{}, strict/lenient joint match, \incCode{}, and document-reference mismatch.

\paragraph{Human validation.}
\label{sec:human-validation}
We released 75 expert-validation records spanning all eight industries, all five difficulty levels, and 15 inconsistency codes. Reviewers were practising finance professionals at two major U.S.\ investment banks and worked from self-contained Markdown records. Records 1--25 were independently double-reviewed. Collapsing acceptable judgments (``Yes''/``Mostly'' or ``Accept''/``Accept with minor fixes'') gives $100\%$ agreement on document analogy, entries, \texttt{doc\_refs}, and the overall verdict, and $96\%$ on difficulty calibration. Strict exact-option agreement is lower where reviewers differ on severity rather than acceptability: $64\%$ on analogy, $96\%$ on entry correctness, $100\%$ on entry completeness, $72\%$ on \texttt{doc\_refs} support, $96\%$ on difficulty, and $80\%$ overall. Separately, a certified accountant independently reviewed the full compact coverage split ($143$ records: $120$ standard + $23$ forced-inconsistency). Because this split contains one record for every industry--period--difficulty cell and one for every inconsistency code, that pass checks each compact scenario at least once. The full-coverage review rejected no record; a small number of records received minor tightening notes on document references or wording, while all $23$ forced-inconsistency records were confirmed to contain a real contradiction. Appendix~\ref{appx:human-protocol} gives the protocol, assignment, and marginals.
