\section{Limitations and Ethics}

The current study has five main limitations.
First, the benchmark is entirely synthetic even though the accounting
mechanics are realistic.
Synthetic control is valuable for exact scoring, but it cannot cover
the full distribution of language, ambiguity, and disclosure
conventions found in live corporate reporting.

Second, the paper now spans two evaluation pools rather than one fully
matched leaderboard.
The main analysis uses the completed 500-problem subset, whereas some
frontier systems are currently available only on the separate
100-problem compatibility subset.
That split is better than mixing incomparable runs, but it means the
paper cannot yet offer a single full-coverage ranking across all
intended models.

Third, proprietary coverage at the larger scale is still incomplete.
GPT-5.2 is currently reported only on the 100-problem compatibility
subset, and the available Large-500 gpt-oss-120b \CoT{} rerun stopped
after \(37\) of \(500\) problems.
We therefore exclude that incomplete run and retain only the
zero-shot gpt-oss-120b compatibility result in the paper.

Fourth, the paper studies statement construction rather than statement
auditing.
In practical accounting workflows, construction and auditing are
complementary, but they require different supervision signals and
evaluation protocols.

Fifth, all experiments in this draft rely on end-to-end language-model
generation, which means the model is responsible for both selecting the
correct accounting operations and performing the arithmetic internally.
Because bookkeeping arithmetic is deterministic, a useful complementary
comparison is a tool-augmented variant in which the model issues typed
function calls to an external calculator or ledger engine while the tool
performs the actual computation.
Such a comparison would clarify how much of current failure is due to
accounting misclassification versus arithmetic execution.

From an ethics perspective, the benchmark should be used as an
evaluation tool rather than evidence that a model is safe for autonomous
accounting use.
Several systems produce fluent, well-structured outputs while violating
the accounting equation or silently mishandling equity closure.
That failure mode is precisely the kind that could evade casual human
inspection.
