\section{Discussion}
\label{sec:discussion}

The central empirical finding is not that frontier LLMs cannot do accounting. It is that capable models produce locally-correct journal entries and then fail to maintain self-consistency between those entries and the balance sheet they report---and that a closed-form feedback signal, applied once, recovers most of what was lost. The same models, in roughly the same inference budget, route around the gap when shown their own ledger deltas. This is a process failure, not a knowledge failure.

The aggregation gap and the document-linking failure are instances of the same phenomenon. Each arises when the model has enough information to produce a correct local component (a balanced entry, an account-correct posting) but is asked to maintain a global property over many such components (the accounting equation across the period, the correct citation among many candidate documents). Each fails despite the underlying component being right. Light deterministic scaffolding---the verifier in one case, oracle filtering in the other---repairs both.

The verifier's mechanism isolates a question that sampling cannot answer cleanly. Best-of-3 with our ledger-aware selector recovers $\sim$40\% of the verifier's gain: three independent samples either contain a correct answer the selector identifies or do not. The verifier instead lets the model \emph{revise}---presented with its own deltas, it edits the existing draft toward consistency. The $\sim$20\,pp \bsexact{} gap between picking and revising is the value of a corrected pass over the model's output rather than another draw from its distribution.

We caution against generalising the verifier beyond settings that admit a closed-form check. Accounting is unusual: the ledger that produces ground-truth labels \emph{is} the verifier. For tasks without such a specification the analogous intervention requires a learned verifier \citep{cobbe2021gsm8k,lightman2024verify} or LM-as-feedback \citep{madaan2023selfrefine,shinn2023reflexion}. Our contribution is narrower: where a task admits a deterministic ground-truth oracle, that oracle can be repurposed at inference time as a scaffold; the size of the resulting gain is informative about how much residual error is process rather than parametric.

The trade-off deserves honest reading: the verifier improves reconciling a clean packet at the cost of detecting an unreconcilable one---a metric benchmarks built only on clean records will not surface. The failure path is not specific to \emph{this} verifier but to any feedback signal conditioning on consistency-with-ledger rather than consistency-with-evidence.
