\section*{Limitations}

\paragraph{Synthetic construction.}
\benchmark{} is synthetic in the way a good controlled benchmark should be: it composes human-authored business scenarios, document schemas, accounting policies, tax and FX assumptions, support-document dependencies, distractors, and contradiction templates, then uses code for the repetitive sampling, rendering, and ledger replay. This gives us inspectable labels and controlled counterfactuals. The limitation is document fidelity: real accounting document bundles contain messier layouts, OCR errors, missing pages, handwriting, ambiguous vendor formats, inconsistent naming, and institution-specific artifacts that our rendered documents only approximate. The benchmark therefore measures reasoning over clean OCR text, not end-to-end document understanding in production systems.

\paragraph{Accounting coverage.}
Accounting is broad and policy-dependent. Our labels are deterministic after fixing the chart of accounts, accounting policy, tax assumptions, and transaction generator. We cover a substantial slice of reconciliation work---multi-document postings, period-end adjustments, tax, foreign exchange, leases, deferred tax, revenue schedules, subledgers, distractors, and forced contradictions---but not the full space of GAAP, IFRS, local tax regimes, materiality judgments, industry-specific policy choices, or audit procedures. The benchmark is intended to open a precise document-grounded accounting setting, not to replace a complete accounting standards corpus.

\paragraph{Analysis depth.}
The ablations reveal several robust patterns, including the aggregation gap, weak gains from prompt-only changes, document-linking failures, context/evidence effects, and the ledger-feedback trade-off with inconsistency detection. We analyse these effects at the behavioral level, but we do not establish the internal mechanisms that cause them, nor whether the same failure modes transfer unchanged to other high-precision domains such as legal reconciliation, insurance claims, or scientific lab records. The released harness is intended to support deeper follow-up studies: larger ablation matrices, controlled perturbations, model-family comparisons, and mechanistic or representation-level analyses of why models fail after the relevant evidence is present.

\paragraph{Evaluation scope.}
Headline numbers use a single temperature-$0$ decoding run except for the best-of-3 condition, so the paper emphasizes large paired effects rather than single-point differences. Six models are evaluated at full $n{=}143$ on baseline; ledger-feedback replication is full on three models and partial on Qwen. The aggregation gap is therefore a consistent pattern across this model panel, not a claim about every language model.

\paragraph{Benchmark longevity.}
The public core split may become contaminated as models train on released benchmarks, a risk shared by most static evaluation sets. \benchmark{} mitigates this by releasing the generator, not only a fixed test file: users can sample fresh seeded document bundles from the same human-authored scenario space, create larger train/test splits, and add new industries, document schemas, policies, contradiction templates, and ablation surfaces without hand-labeling every record. We version the released split for comparability; long-term validity comes from periodically generated held-out document bundles and community extensions of the scenario library.

\paragraph{Ethics and AI assistance.}
The benchmark uses synthetic data; no real records, PII, or production accounting data are used. The ARR Responsible NLP checklist is completed in the submission materials; Appendix~\ref{appx:reproducibility} reports reproducibility and release details only. We used generative-AI assistance for coding support and for grammar, wording, and formatting edits while drafting. The benchmark idea, accounting logic, experimental design, result interpretation, paper argument, and final claims were authored and controlled by humans. We did not use AI assistance to create hidden reviewer-facing prompts or instructions intended to manipulate reviewers.
